---
title: "Project title"
author: "Author"
date: "Time period when project was undertaken"
output: 
  html_document:
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview {.tabset}

### Background and aims

* Brief description of the topic / issue that the work looked at.

* What were the overall aims of the piece of work? e.g. Gain insight, automate a process, encourage best practice. 

### Teams and individuals 

* Who did we work with? (This can include third-party teams that we worked with during the project)
* Who in the Data team worked on the project?
* Best person to query?


## Software and methods {.tabset}

### Software

* Software - include versions (e.g. R version 3.5.1)
* Add-ons required (e.g. R packages or BI Visualisations) - include versions if relevant (e.g. "ggplot version 2.2.1
                                                              used because version 3.0.0 conflicted with package X")

### Databases (optional)

* Did the data come from a specific database?
* How was the data accessed?

### Method

* A high-level guide to what method was used. Rather than a step-by-step, describe the broader steps taken and include any code for reference. Where possible, give the reader an idea of what the data looked like. For example: 

The data was imported into RStudio and transformed from wide to long format. 

```{r message = FALSE, warning=FALSE}
library(readxl)
library(magrittr)
library(tidyverse)
data <- read_csv("my_spreadsheet.csv") %>%
  gather("January":"December", key = "Month", value = "page_views")

head(data)
```



### Additional Notes
* A brief note on why we chose this software and method - was there a decision process? 
* Alternative approaches that we were not chosen and why 
* Potential approaches that could be explored in future
* Anything else that might be relevant 

### Feedback
Detail here any relevant feedback from external teams about **the method itself**. For example:

* What worked well?
* Did anything not make sense? 



